### 2017-08-25 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic XRD - Added to the draft

The bulk is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and film in Figure \ref{fig:XRD_Dynamic_Film}.

@@

In the bulk a double peak at 38\degree~ and 39\degree~ begins to emerge at 125\degree C, phases which never evolve in the film. The bulk \CaMgZnFive~ peaks at 42.3\degree~ and 43.7\degree~ start to emerge at 165\degree C and 170\degree C respectively, but are never seen in the film. The small 57.2\degree~ peak at 170\degree C is also never seen in the film. A final faint peak at 53.3\degree is seen in the bulk at 175\degree C but never in the film. These observations are tabulated in Table \ref{tab:Dynamic_XRD}.

>>>>

@@

In the bulk a double peak at 38\degree~ and 39\degree~ begins to emerge at 125\degree C, phases which never evolve in the film. The bulk \CaMgZnFive~ peaks at 42.3\degree~ and 43.7\degree~ start to emerge at 165\degree C and 170\degree C respectively, but are never seen in the film. The small 57.2\degree~ peak at 170\degree C is also never seen in the film. A final faint peak at 53.3\degree is seen in the bulk at 175\degree C, but never in the film. These observations are tabulated in Table \ref{tab:Dynamic_XRD}. The bulk \acrshort{xrd} is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and the film in Figure \ref{fig:XRD_Dynamic_Film}. Normalised plots allowing for easy identification of differences between the bulk and film are shown in Figures \ref{fig:XRD_Dynamic_185}, \ref{fig:XRD_Dynamic_145}, and \ref{fig:XRD_Dynamic_105}.
